Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary

### 2024-01-29 manu-draft.qmd
add orcid to author yaml

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      institute: [TBEP]
      correspondence: false
  - Bradley T Furman:
      email: Bradley.Furman@myfwc.com
      institute: [FWRI]
      correspondence: false
  - David J Karlen: 
      email: karlen@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Chris Pratt: 
      email: prattc@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Edward T Sherwood:
      email: esherwood@tbep.org
      institute: [TBEP]
      correspondence: false

>>>>

---
format: 
  docx:
    reference-doc: my_styles.docx
    number-sections: true
title: "Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary"
bibliography: refs.bib
csl: estuaries-and-coasts.csl
author:
  - Marcus W Beck:
      email: mbeck@tbep.org
      orcid: 0000-0002-4996-0059
      institute: [TBEP]
      correspondence: true
  - Kerry Flaherty-Walia:
      email: kfwalia@tbep.org
      orcid: 0000-0002-6032-0570
      institute: [TBEP]
      correspondence: false
  - Sheila Scolaro:
      email: sscolaro@tbep.org
      orcid: 0000-0003-3220-3737
      institute: [TBEP]
      correspondence: false
  - Maya C Burke:
      email: mburke@tbep.org
      orcid: 0000-0002-3847-6501      
      institute: [TBEP]
      correspondence: false
  - Bradley T Furman:
      email: Bradley.Furman@myfwc.com
      orcid: 0000-0002-9284-8388
      institute: [FWRI]
      correspondence: false
  - David J Karlen: 
      email: karlen@epchc.org
      orcid: 0000-0002-1432-9099
      institute: [EPCHC]
      correspondence: false
  - Chris Pratt: 
      email: prattc@epchc.org
      institute: [EPCHC]
      correspondence: false
  - Edward T Sherwood:
      email: esherwood@tbep.org
      orcid: 0000-0001-5330-302X
      institute: [TBEP]
      correspondence: false
